Automated Topic Naming

### 2011-09-02 ese/ese.tex
supervised numbers and plot now accurate

The range of F-measures for MySQL was $0.21$ to $0.77$ with a mean
of $0.48$. MaxDB had a range of $0.17$ to $0.61$ with a mean
\todo{NE: I believe these numbers are wrong}
of $0.39$. Finally, PostgreSQL had a range of $0.58$ to $0.69$ and a mean of $0.64$.

>>>>

%src/validate/latex-out/best-learner-per-project-roc
The range of F-measures for MySQL was $0.21$ to $0.77$ with a mean
of $0.48$. MaxDB had a range of $0.17$ to $0.61$ with a mean
of $0.39$. Finally, PostgreSQL had a range of $0.04$ to $0.9$ and a mean of $0.43$.
